### 2007-01-14 Documentation/part1.tex
JK - Minor corrections in chapter 7

\example{The impact of systematics, correlations, and degeneracies}{
\label{ex:barcharts}
\index{norm}{Bar plots}
\index{norm}{Systematics!on/off}
Here it is demonstrated how one can successively include systematics, correlations, and degeneracies at the example of the $\stheta$-sensitivity limit.
An important part of this example is how two switch the systematics off,
\ie, how to obtain the sensitivity limit from statistics only. Since
this example is very advanced, we only show the respective function of the code:
\begin{quote}
{\tt 
/* Calculate chi2 with statistics only */ \\
double CalcNoSystematics(double theldm,double thex) \\
\{ \\
\hspace*{0.5cm} /* Switch systematics off for all exps and all rules */ \\
\hspace*{0.5cm} glbSwitchSystematics(GLB\_ALL,GLB\_ALL,GLB\_OFF); \\
\\
\hspace*{0.5cm} /* Calculate Chi2-list as if systematics were on */ \\
\hspace*{0.5cm} double res=CalcSystematics(theldm,thex); \\
\\
\hspace*{0.5cm} /* Switch systematics on for all exps and all rules */ \\
\hspace*{0.5cm} glbSwitchSystematics(GLB\_ALL,GLB\_ALL,GLB\_ON); \\
\\
\hspace*{0.5cm} return res; \\
\} \\
}
\end{quote}

@@

The complete code can be found as {\tt example4.c} with the software,
which consists of many of the applications from the earlier examples.
In addition, it uses a little trick: It avoids falling into the wrong
 solution with {\tt glbChiTheta13}
by using the fit value of $\deltacp$ from the step before as prediction
of the position of the current calculation.

The returned lists of data from the example represent $\chi^2$ 
as function of the fit value of $\stheta$. The intersections of these
curves with the line $\chi^2 = 9$ give the $\stheta$ sensitivity
limits at the $3 \sigma$ confidence level, where we do not include the
 $\mathrm{sgn}(\ldm)$- and $(\deltacp,\theta_{13})$-degeneracies in the sensitivity limit with correlations only (green bar):
\begin{center}
\colorbox{white}{\includegraphics[width=6.5cm]{barsex}}
\end{center}
}

@@

Using external parameters in \AEDL\ files is a very powerful feature
to change experiment parameters at running time which require that
the experiment be re-initialized. For example, one can change the
energy resolution function or the number of energy bins. However,
in some cases there might be complications, such that the number
of pre- or post-smearing efficiencies does not correspond to the number
of energy bins anymore. Therefore, this feature needs to be 
used with care.

@@

In order to use the user-defined variable, one has to assign it 
with {\tt glbDefineAEDLVariable} {\em before} the experiment is initialized with \GLB{InitExperiment}:
\begin{function}
\GLBNS{DefineAEDLVariable}
{\tt void glbDefineAEDLVariable(const char* name, double value)}
assigns the value {\tt value} to the \AEDL\ variable {\tt name}.
\end{function}
In our energy resolution example, one could now loop over the
energy resolution such as with
\begin{quote}
{\tt
int i; \\
for(i=5;i<20;i++) \\
\{ \\    
\hspace*{1cm} glbClearExperimentList(); \\
\hspace*{1cm} glbDefineAEDLVariable("myres",0.01*i); \\
\hspace*{1cm} glbInitExperiment(...); \\
\\
\hspace*{1cm} /* do something */ \\
\}
}
\end{quote}
Note that one does not have do re-initialize the oscillation
parameter vectors every time within the loop as long as the
number of experiments does not change.

>>>>

\example{The impact of systematics, correlations, and degeneracies}{
\label{ex:barcharts}
\index{norm}{Bar plots}
\index{norm}{Systematics!on/off}
Here, we demonstrate how systematics, correlations, and degeneracies
can be succesively included in the calculation of the $\stheta$-sensitivity limit.
The following code fragment shows how systematics can be switched off
in order to compute the sensitivity limit from statistics only:
\begin{quote}
{\tt 
/* Calculate chi2 with statistics only */ \\
double CalcNoSystematics(double theldm,double thex) \\
\{ \\
\hspace*{0.5cm} /* Switch systematics off for all exps and all rules */ \\
\hspace*{0.5cm} glbSwitchSystematics(GLB\_ALL,GLB\_ALL,GLB\_OFF); \\
\\
\hspace*{0.5cm} /* Calculate Chi2-list as if systematics were on */ \\
\hspace*{0.5cm} double res=CalcSystematics(theldm,thex); \\
\\
\hspace*{0.5cm} /* Switch systematics on for all exps and all rules */ \\
\hspace*{0.5cm} glbSwitchSystematics(GLB\_ALL,GLB\_ALL,GLB\_ON); \\
\\
\hspace*{0.5cm} return res; \\
\} \\
}
\end{quote}

@@

The complete code is very advanced and can be found in {\tt example4.c}.
It includes many concepts from earlier examples, and, in addition,
it uses a little trick: It avoids falling into the wrong solution with
{\tt glbChiTheta13} by using the fit value of $\deltacp$ from the step
before as prediction for the position of the minimum in the current calculation.

The returned lists of data from the example represent $\chi^2$ 
as function of the fit value of $\stheta$. The intersections of these
curves with the line $\chi^2 = 9$ give the $\stheta$ sensitivity
limits at the $3 \sigma$ confidence level. Note that, in the following
plot, the $\mathrm{sgn}(\ldm)$- and $(\deltacp,\theta_{13})$-degeneracies
are not included in the sensitivity limit with correlations only (green bar),
but only in the limit with degeneracies (yellow bar):
\begin{center}
\colorbox{white}{\includegraphics[width=6.5cm]{barsex}}
\end{center}
}

@@

Using external parameters in \AEDL\ files is a very powerful feature
to change experiment parameters at running time, which requires, however, that
the experiment be re-initialized. For example, one can change the
energy resolution function or the number of energy bins. However,
in some cases, there might be complications, such that the number
of pre- or post-smearing efficiencies does not correspond to the number
of energy bins anymore. Therefore, this feature needs to be 
used with care.

@@

In order to use the user-defined variable, one has to assign it 
with {\tt glbDefineAEDLVariable} {\em before} the experiment is initialized with \GLB{InitExperiment}:
\begin{function}
\GLBNS{DefineAEDLVariable}
{\tt void glbDefineAEDLVariable(const char* name, double value)}
assigns the value {\tt value} to the \AEDL\ variable {\tt name}.
\end{function}
In our energy resolution example, one could now loop over the
energy resolution such as with
\begin{quote}
{\tt
int i; \\
for(i=5;i<20;i++) \\
\{ \\    
\hspace*{1cm} glbClearExperimentList(); \\
\hspace*{1cm} glbDefineAEDLVariable("myres",0.01*i); \\
\hspace*{1cm} glbInitExperiment(...); \\
\\
\hspace*{1cm} /* do something */ \\
\}
}
\end{quote}
Note that one does not have to re-initialize the oscillation
parameter vectors every time within the loop as long as the
number of experiments does not change.
